Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-13 write-ups/PLDI/paper.tex
typo
Edit "the gpu we tested"

\begin{table}
\small
\centering
\begin{tabular}{ l c c c }
app & resizing barriers & ckill - cfork & tranmit vars\\
\hline
\rowcolor{Gray1}
color & 2 / 2 & 0 - 0 & 4\\
\rowcolor{Gray1}
mis & 3 / 3 & 0 - 0 & 0\\
\rowcolor{Gray1}
bc & 3 / 6 & 0 - 0 & 3\\
\rowcolor{Gray1}
p-sssp & 3 / 3 & 0 - 0 & 0 \\
\rowcolor{Gray2}
bfs & 2 / 2 & 0 - 0  & 4 \\
\rowcolor{Gray2}
l-sssp & 2 / 2 & 0 - 0  & 4 \\
\rowcolor{Gray3}
octree & 0 / 0 & 1 - 1 & 0\\
\rowcolor{Gray3}
game & 0 / 0 & 1 - 1 & 0\\
\end{tabular} \\
\vspace{.2cm}
\crule[Gray1]{.2cm}{.2cm} - Pannotia \hspace{.4cm} \crule[Gray2]{.2cm}{.2cm} - Lonestar GPU  \hspace{.4cm}  \crule[Gray3]{.2cm}{.2cm} - work stealing
\caption{Blocking GPU applications investigated}
\label{tab:applications}
\end{table}

@@

Our implementation approach requires two optional features of OpenCL
$2.0$, namely SVM fine-grained buffers and SVM atomics, which are
currently not widely supported. \nvidia chips are ruled out since
\nvidia does not support OpenCL $2.0$. AMD support SVM atomics only
their Kaveri family of chips and only on Linux, requiring to compile the
latest driver.  \HEComment{do we need to mention the struggle for AMD ?}
Among the GPUs available to us, only 4 support our requirements: Intel
HD 520, HD 5500 and IRIS 6100, and AMD Radeon R7.

>>>>

\begin{table}
\small
\centering
\begin{tabular}{ l c c c }
app & resizing barriers & ckill - cfork & transmit vars\\
\hline
\rowcolor{Gray1}
color & 2 / 2 & 0 - 0 & 4\\
\rowcolor{Gray1}
mis & 3 / 3 & 0 - 0 & 0\\
\rowcolor{Gray1}
bc & 3 / 6 & 0 - 0 & 3\\
\rowcolor{Gray1}
p-sssp & 3 / 3 & 0 - 0 & 0 \\
\rowcolor{Gray2}
bfs & 2 / 2 & 0 - 0  & 4 \\
\rowcolor{Gray2}
l-sssp & 2 / 2 & 0 - 0  & 4 \\
\rowcolor{Gray3}
octree & 0 / 0 & 1 - 1 & 0\\
\rowcolor{Gray3}
game & 0 / 0 & 1 - 1 & 0\\
\end{tabular} \\
\vspace{.2cm}
\crule[Gray1]{.2cm}{.2cm} - Pannotia \hspace{.4cm} \crule[Gray2]{.2cm}{.2cm} - Lonestar GPU  \hspace{.4cm}  \crule[Gray3]{.2cm}{.2cm} - work stealing
\caption{Blocking GPU applications investigated}
\label{tab:applications}
\end{table}

@@

Our implementation approach requires two optional features of OpenCL
$2.0$, namely SVM fine-grained buffers and SVM atomics, which are
currently not widely supported. \nvidia chips are ruled out since
\nvidia does not support OpenCL $2.0$. Intel drivers meet our
requirements on Windows, but not on Linux, although we tried the
upstream driver that requires a patched Linux kernel. AMD support SVM
atomics only their Kaveri family of chips and only on Linux, requiring
to compile the latest driver. Among the GPUs available to us, only 4
turned out to provide our requirements: Intel HD 520, HD 5500 and IRIS
6100, and AMD Radeon R7.

\HEComment{To decide: do we mention carrot AMD, in which terms?}
